Variable Selection in Convex Function Estimation

### 2013-10-04 tex/scam/appendix.tex
appendix update

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k d_k 
       + c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( r_k - \Delta_k d_k 
       + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

@@

\begin{align*}
-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u} 
           - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
-\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
where $\mathbf{u}$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.

First, we observe that $\gamma_k = 0$ because $\hat{r}$ has empirical mean 0. All we need to prove then is that 
\[
\lambda \mathbf{u} - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
\]

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.

@@

\begin{align*}
\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}) 
                                            - \frac{1}{n} \hat{r}^\tran X_{k(j)} \\
                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})
\end{align*}
Our goal in this proof is to bound $\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})$ from above.

@@

For a fixed $f'$, we have that, by definition
\begin{align*}
\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0\mathbf{1}_n - \bar{w} \mathbf{1}_n - f' \|_n^2\\
     &= \| f_0  - \bar{f}_0\mathbf{1}_n - f'\|_n^2 
       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n - f'\rangle_n + \| w \|_n^2 + |\bar{w}|\\
R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
     &= \E\big(f_0(X) - \mu - f'(X)\big)^2 + \E w^2  
\end{align*}

@@

\begin{proposition} (Subexponential Concentration \cite{vershynin2010introduction})
Let $X_1,...,X_N$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
\[
P( | \frac{1}{N} \sum_{i=1}^N X_i | \geq \epsilon) \leq
	2 \exp \left[ -c N \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) \right]
\]
where $c > 0$ is an absolute constant.
\end{proposition}

@@

\textbf{Restating}. We can set
\[
c \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) = \frac{1}{N} \log \frac{1}{\delta}.
\]
Thus, with probability at least $1-\delta$, the deviation at most
\[
K \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}},  \frac{1}{cn} \log \frac{C}{\delta} \right)
\]

@@

A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.s

>>>>

\begin{align*}
\partial d_k :& \qquad -\frac{1}{n} \Delta_k^\tran ( r_k - \Delta_k d_k 
       + c_k \mathbf{1}) + \lambda \mathbf{u}_k  - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} \\
\partial c_k: & \qquad -\frac{1}{n} \mathbf{1}^\tran ( r_k - \Delta_k d_k 
       + c_k \mathbf{1}) + \gamma_k
\end{align*}
In the derivatives, $\mathbf{u}_k$ is a $(n-1)$-vector whose first coordinate is $\partial | d_{k1}|$ and all other coordinates are 1.

@@

\begin{align*}
-\frac{1}{n} \Delta_k^\tran\hat{r} + \lambda \mathbf{u}_k 
           - \mu_k - \gamma_k \Delta_k^\tran \mathbf{1} &= 0 \\
-\frac{1}{n} \mathbf{1}^\tran \hat{r} + \gamma_k & = 0 \\
\end{align*}
where $\mathbf{u}_k$ is 1 in every coordinate except the first, where it can take any value in $[-1,1]$.

First, we observe that $\gamma_k = 0$ because $\hat{r}$ has empirical mean 0. All we need to prove then is that 
\[
\lambda \mathbf{u}_k - \mu_k = \frac{1}{n} \Delta_k^\tran \hat{r}.
\]

Suppose
\[
\lambda \mathbf{1} > |\frac{1}{n} \Delta_k^\tran\hat{r}|,
\]
then we easily see that the first coordinate of $\mathbf{u}_k$ can be set to some value in $(-1,1)$ and we can set $\mu_{k,i} > 0$ for $i=2,...,n$.

@@

\begin{align*}
\frac{1}{n} \hat{r}^\tran \Delta_{k,j} &= 
              \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)}\mathbf{1}_n) 
                                       - \frac{1}{n} \hat{r}^\tran \mathbf{1}_n X_{k(j)} \\
                  &= \frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})
\end{align*}
Our goal in this proof is to bound $\frac{1}{n} \hat{r}^\tran \max(X_k, X_{k(j)})$ from above.

@@

For a fixed $f'$, we have that, by definition
\begin{align*}
\hat{R}_s (f') &= \| f_0 + w - \bar{f}_0\mathbf{1}_n - \bar{w} \mathbf{1}_n - f' \|_n^2\\
     &= \| f_0  - \bar{f}_0\mathbf{1}_n - \bar{w}\mathbf{1}_n - f'\|_n^2 
       + 2 \langle w, f_0 - \bar{f}_0\mathbf{1}_n -\bar{w}\mathbf{1}_n - f'\rangle_n 
       + \| w \|_n^2 \\
R_s(f') &= \E\big(f_0(X) + w - \mu - f'(X)\big)^2 \\
     &= \E\big(f_0(X) - \mu - f'(X)\big)^2 + \E w^2  
\end{align*}

@@

\begin{proposition} (Subexponential Concentration \cite{vershynin2010introduction})
Let $X_1,...,X_n$ be zero-mean independent subexponential random variables with subexponential scale $K$. 
\[
P( | \frac{1}{n} \sum_{i=1}^n X_i | \geq \epsilon) \leq
	2 \exp \left[ -c n \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) \right]
\]
where $c > 0$ is an absolute constant.
\end{proposition}

@@

\textbf{Restating}. We can set
\[
c \min\left( \frac{\epsilon^2}{K^2}, \frac{\epsilon}{K} \right) = \frac{1}{n} \log \frac{1}{\delta}.
\]
Thus, with probability at least $1-\delta$, the deviation at most
\[
K \max\left( \sqrt{\frac{1}{cn} \log \frac{C}{\delta}},  \frac{1}{cn} \log \frac{C}{\delta} \right)
\]

@@

A simple restatement. With probability at least $1- \delta$, the deviation $| \frac{1}{N} S_n|$ is at most $ (b-a) \sqrt{ \frac{1}{2N} \log \frac{2}{\delta}}$.
